---
title: "Demonstration of report lay-out. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog."
author: "Thierry Onkelinx, Ivy Jansen, Pieter Verschelde, Hans Van Calster, Toon Westra, Toon Van Daele, Floris Vanderhaeghe, Els Lommelen & Paul Quataert"

output: 
  INBOmd::inbo_rapport_2015:
    subtitle: "The subtitle: The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog."
    reportnr: "INBO.R.2015.1234567890"
    ordernr: "ANB.2014-01234569"
    usepackage: "lipsum"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Demonstration INBO corporate style for reports version 2015}
  %\VignetteDepends{pander}
  %\VignetteDepends{ggplot2}
  %\SweaveUTF8
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(message = FALSE)
```

# Heading styles: level 1: The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

\lipsum[1-2]

## Level 2: The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

\lipsum[3-4]

### Level 3:The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

\lipsum[5-6]

#### Level 4: The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

\lipsum[7-8]

##### Level 5: The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

\lipsum[9-10]

###### Level 6: The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

\lipsum[11-12]














\chapter*{Heading styles without numbering: level 1: The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.}
\section*{Level 2: The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.}
\subsection*{Level 3: The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.}
\subsubsection*{Level 4: The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.}
\paragraph*{Level 5: The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.}
\subparagraph*{Level 6: The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.}







# Font styles

## Normal

\lipsum[13-14]

## Bold

**\lipsum[15-16]**

## Italics

_\lipsum[17-18]_

##Bold italics

**_\lipsum[19]_**

_**\lipsum[20]**_

## Monospace

`The quick brown fox jumps over the lazy dog.`

**`The quick brown fox jumps over the lazy dog.`**

_`The quick brown fox jumps over the lazy dog.`_

**_`The quick brown fox jumps over the lazy dog.`_**

`The quick` **`brown`** `fox` _`jumps`_ `over the` **_`lazy`_** `dog.`

\texttt{\lipsum[21-22]}

## Small L versus capital i

normal:
  ~ lI

bold:
  ~ **lI**
  
italics:
  ~ _lI_

bold italics:
  ~ **_lI_**

monospace:
  ~ `lI` **`lI`** _`lI`_ **_`lI`_** 

## Special characters
  
### Normal

€$£ @&#§µ^ ()[]{}|²³<>/\*+- ,;:.?!~ äàáâã ëèéê ïìíî öòóô üùúû ÿ ç ñ ÄÀÁÂ ËÈÉÊ ÏÌÍÎ ÖÒÓÔ ÜÙÚÛ Ñ 0123456789

### Bold
**€$£ @&#§µ^ ()[]{}|²³<>/\*+- ,;:.?!~ äàáâã ëèéê ïìíî öòóô üùúû ÿ ç ñ ÄÀÁÂ ËÈÉÊ ÏÌÍÎ ÖÒÓÔ ÜÙÚÛ Ñ 0123456789**

### Italics
_€$£ @&#§µ^ ()[]{}|²³<>/\*+- ,;:.?!~ äàáâã ëèéê ïìíî öòóô üùúû ÿ ç ñ ÄÀÁÂ ËÈÉÊ ÏÌÍÎ ÖÒÓÔ ÜÙÚÛ Ñ 0123456789_

### Bold italics
**_€$£ @&#§µ^ ()[]{}|²³<>/\*+- ,;:.?!~ äàáâã ëèéê ïìíî öòóô üùúû ÿ ç ñ ÄÀÁÂ ËÈÉÊ ÏÌÍÎ ÖÒÓÔ ÜÙÚÛ Ñ 0123456789_**
  
### Monospace
`€$£ @&#§µ^ ()[]{}|²³<>/\*+- ,;:.?!~ äàáâã ëèéê ïìíî öòóô üùúû ÿ ç ñ ÄÀÁÂ ËÈÉÊ ÏÌÍÎ ÖÒÓÔ ÜÙÚÛ Ñ 0123456789`

## Quotes

normal:
  ~ "double quotes", 'single quotes'

bold:
  ~ **"double quotes", 'single quotes'**

italics:
  ~ _"double quotes", 'single quotes'_

bold italics:
  ~ **_"double quotes", 'single quotes'_**

monospace:
  ~ `"double quotes", 'single quotes',` **`"double quotes", 'single quotes',`** _`"double quotes", 'single quotes',`_ **_`"double quotes", 'single quotes'`_**


# Listings

## Itemize

- \lipsum[36]
- Item 2
- Item 3
    - Item a
        - item I
        - item II
            - item A
            - item B
            - \lipsum[39]
        - \lipsum[38]
    - \lipsum[37]
    - Item c
- Item 4

## Enumerate

1. \lipsum[32]
1. Item 2
1. Item 3
    1. Item a
        1. item I
        1. item II
            1. \lipsum[35]
            1. item B
            1. item C
        1. \lipsum[34]
    1. \lipsum[33]
    1. Item c
1. Item 4

## Description

Item A
  ~ \lipsum[23]
  
Longer item title B
  ~ \lipsum[24]
  
    Item B1
      ~ \lipsum[27]

        Item B1a
          ~ \lipsum[29]

        Item B1b
          ~ \lipsum[30]

            Item B1b1
              ~ \lipsum[31]
              
    Item B2
      ~ \lipsum[28]

Item C
  ~ \lipsum[25]
  
Item D
  ~ \lipsum[26]

# Blocks

## Block

\begin{block}{The quick brown fox jumps over the lazy dog.}
  \lipsum[40-41]
\end{block}


## Exampleblock
  
\begin{exampleblock}{The quick brown fox jumps over the lazy dog.}
  \lipsum[42-43]
\end{exampleblock}

## Alertblock

\begin{alertblock}{The quick brown fox jumps over the lazy dog.}
\lipsum[44-45]
\end{alertblock}

# R Code

## Code
```{r datasets, error = TRUE, message = TRUE}
c(TRUE, FALSE)
c(0, 1)
c(0.0, 1.0)
c(1e-10, 1e10)
c("Monday", "Tuesday", "Wednesday")
factor(c("Monday", "Tuesday", "Wednesday"))
example <- data.frame(
  Day = c("Monday", "Tuesday", "Wednesday"),
  'Min Temp' = c("11C", "9C", "10C"),
  'Max Temp' = c("22C", "19C", "21C"),
  Summary = c(
    "A clear day with lots of sunshine. However, the strong breeze 
    will bring down the temperatures.", 
    "Cloudy with rain, across many northern regions. Clear spells 
    across most of Scotland and Northern Ireland, but rain reaching the far northwest.", 
    "Rain will still linger for the morning. Conditions will improve 
    by early afternoon and continue throughout the evening."
  )
)
str(example)
my_fun <- function(x){
  cat("my function is", x)
}
my_fun("cool")
message("just a message")
warning("this is a warning")
stop("this is an error message")
```

## Tables and figures

### Tables

#### Multiline table

```{r multiline_table, results='asis'}
library(pander)
pandoc.table(example)
```

#### Grid table

```{r grid_table, results='asis'}
pandoc.table(example, style = "grid")
```

### Figures

```{r, fig.cap= "Histogram of movie rating per MPAA rating"}
library(ggplot2)
ggplot(movies, aes(x = rating)) + 
  geom_histogram() + 
  facet_wrap(~mpaa, scales = "free")
```

```{r, fig.cap= "Histrogram of the price per diamond per cut"}
ggplot(diamonds, aes(x = price, fill = cut)) + 
  geom_histogram()
```

```{r, fig.cap= "Relation between miles per gallon and weight for cars from 1974, split by number of cylinders."}
ggplot(
  mtcars, 
  aes(x = wt, y = mpg, colour = factor(cyl), fill = factor(cyl))
) +
  geom_point() + 
  geom_smooth(method = "lm")
```

